\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2020-09-25 redaction/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Debug prix fob + chgt texte

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows from \textbf{1989 to 2019}. First, we document the importance of the per-unit component of transport costs. It represents between one-third and one-half of overall transport costs. Second, allowing for time-varying per-unit costs, we find that the downward trend in international transport costs comes from the reduction in “pure” transport costs over time, with trade composition effects playing a minor role. In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
\end{abstract}

@@

Our results may be summarized in two main new findings.
First, additive transport costs are quantitatively sizable.
On average over \textbf{1989-2019}, the additive cost is estimated to be \textbf{1.8\% and 2.9\% A AJUSTER} of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component \textbf{(2.5\% and 3.2\% for air/vessel} respectively on average over the period).
Put differently, additive costs represent between \textbf{one-third and almost one-half} of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by roughly a \textbf{factor~2}. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

Second, we find that the main source of the downward trend in overall transport costs comes mainly from the reduction of transport cost \textit{per se}, , by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2013}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} This contrasts with the conclusion obtained by \citet{hummels2007} yet also on US imports flows.\footnote{Both Hummel's and our's databases come from the US Bureau of Census's import flows database, with two differences yet. While Hummels considers products at the 5-digit classification level, we are able to exploit heterogeneity in the data at the much more disaggregated HS-10 level. Second, as US imports data at the HS-10 level are only available since 1989, we run the analysis over 1989-2019, versus 1974-2004 in \citet{hummels2007}. }\textbf{Parler de marge extensive - intensive} \citet{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. In contrast, we find that trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs. Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turn out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period. \textbf{A FAIRE DANS LES REGRESSIONS, METHODE Hummels mais avec s=3, k=10. Peut-on le faire? For the argument to be convincing, need to do it on the same years with the same sector-product degrees.}

@@

Our analysis of transportation costs consists of exploiting the difference between commodity-level export and import prices, as in \citet{hummels2007}. The database we use to construct our measure of transport costs comes from the US annual ``Imports of Merchandise'' provided by the US Census Bureau, spanning 1974 to 2013 (details on the database provided in Appendix \ref{app:data}). We first use customs values, quantities and freight costs to recover free alongside ship (fas) and cost-insurance-freight (cif) prices, by good, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob (free on board) price rather than the fas price. The fas price means that the seller must transport the goods all the way to the dock, close enough to be reached by the crane of the ship it will be transported in. It is also the seller's responsibility to clear the goods for export. The FOB price means that the seller is obligated to bring the goods all the way to the port, clear the goods for export, and see that they are loaded onto the ship nominated by the buyer. Once the goods clear the railing of the vessel, the buyer assumes the risk. Note that this term is used exclusively for maritime and inland waterway transport. While both terms are closely related, the US Foreign Trade Statistics reports fas prices.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight, \textbf{both items being conditional to the transport mode}; in other words, it is the price for one kg of the goods net of transportation costs, \textbf{by transport mode}. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. \textbf{Cf point 2 refere 1 sur unit prices; avoir quantite plutot que poids, robustesse a faire sur sous-echantillon des produits qui ne passent que par un seul mode de transport).} Our dependant variable is finally computed as the ratio of the cif price divided by the fas price.
By construction higher than 1, the variable provides a measure of transport costs as a proportion of the goods' price, an ad-valorem equivalent.
This is quite a standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

Exploiting this dataset also has three advantages.
First, it comes from a single, homogenous and trustworthy customs source.
This limits the measurement error bias.
Based on customs declarations, the US Imports Database inventories all imports (both values and quantities), by country of origin, to the United States at the HS 10-digit level, with a concordance code to the SITC coding system.
%This will be crucial to compute transport costs, as we detail below.
In addition, the database reports information regarding freight, insurance and handling expenditures by transportation mode, land/ocean (or ``vessel'') and air.
We will make use of this to highlight potential differences in the dynamics of transport costs across transportation mode.
Second, this dataset provides both the import price and the export price for the same good (for a given origin country).
This is highly valuable, as it gives us a direct measure of international transport costs (at the country/sector level), from which we can estimate separately the \textit{levels} of both the iceberg costs and of the additive costs, in contrast to e.g. \citet{Irrazabal_2015}.
Third, this dataset is available over a long time span, which enables us to analyze the trend patterns of international transport costs over the period \textbf{1989-2019}.\footnote{Note that, as mentioned by \citet{Lafourcade_Thisse}, our transport costs measures are based on actual trade flows, i.e.
ignoring those flows that did not happen because of presumably prohibitive transport costs.
In light of this, the estimated values that we obtain can be viewed as the lower bounds of the ``potential'' transport costs.} \smallskip

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. We estimate international transport costs at the 3-digit classification level, \textbf{exploiting heterogeneity between HS-10 products.} \textbf{La robustesse en 4/10 peut-elle marcher? sur les premieres annees pour lesquelles moins de points - je crois? Que faire de cette analyse 4d?}
However, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years.\footnote{The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013.
Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation.
However, we obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels.
Estimation results at the 4-digit classification level are reported in Appendix \ref{app:4digit}.} Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin.

@@

\paragraph{Estimation strategy} Our purpose is to provide time-varying estimates of the size of ad-valorem transport costs and additive transport costs.
To do so, denote by $p$ the price per kg of goods paid by the importer (import, or cif price), $\widetilde{p}$ the (per kg) export (or fas) price and $f$ the shipping charge per kg shipped. In accordance with \citet{hummels2010}, we assume that shipping charges may depend on the price $\widetilde{p}$, such that per kg shipping charges are written as $f = \widetilde{p}^{1-\beta} X$, where $X$ represents all other elements of transport costs (such as distance, port quality, etc.). In this case, the link between the import, export prices and shipping charges is given by:

@@

\textbf{While many in the related literature provide an indirect measure of additive costs by estimating the elasticity of freight charges to the unit price (\citealp{hummels_skiba}, \citealp{Lashkaripour-2018}), thereby relying on Equation (\ref{eq:alternative}), we follow another route. Specifically, we start from Equation (\ref{eq:tt2}) and exploit our dataset to obtain an explicit measures of both transport costs components $\tau$ and $t$ (or $\widetilde{t}$). From this, we can deduce the price-elasticity of transport costs, i.e. the share of additive costs in total transport costs.}\smallskip

@@

\textbf{stop here. Pb sur 1+ ...}

\begin{equation}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = \tau_{ik} +\frac{t_{ik}}{ \widetilde{p}_{ik}} \label{eq:base_estimee}
\end{equation}

>>>>

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows from \textbf{1974 to 2019}. First, we document the importance of the per-unit component of transport costs. It represents between one-third and one-half of overall transport costs. Second, allowing for time-varying per-unit costs, we find that the downward trend in international transport costs comes from the reduction in “pure” transport costs over time, with trade composition effects playing a minor role. In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
\end{abstract}

@@

Our results may be summarized in two main new findings.
First, additive transport costs are quantitatively sizable.
On average over \textbf{1974-2019}, the additive cost is estimated to be \textbf{1.8\% and 2.9\% A AJUSTER} of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component \textbf{(2.5\% and 3.2\% for air/vessel} respectively on average over the period).
Put differently, additive costs represent between \textbf{one-third and almost one-half} of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by roughly a \textbf{factor~2}. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

Second, we find that the main source of the downward trend in overall transport costs comes mainly from the reduction of transport cost \textit{per se}, , by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2013}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} This contrasts with the conclusion obtained by \citet{hummels2007} yet also on US imports flows.\footnote{Both Hummel's and our's databases come from the US Bureau of Census's import flows database, with two differences yet. First, we consider a larger period of time, spanning from 1974 (as in \citet{hummels2007}) to 2019 (while he stops in 2004). Second, while Hummels considers products at the 5-digit classification level, we are able to exploit heterogeneity in the data at the much more disaggregated HS-10 level for the vast majority of the period (1989-2019). For the period 1974-1988, we rely on Hummel's original database with a 5-digit product classification level.}\textbf{Parler de marge extensive - intensive} \citet{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. In contrast, we find that trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs. Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turn out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period. \textbf{A FAIRE DANS LES REGRESSIONS, METHODE Hummels mais avec s=3, k=10. Peut-on le faire? For the argument to be convincing, need to do it on the same years with the same sector-product degrees.}

@@

Our analysis of transportation costs consists of exploiting the difference between commodity-level export and import prices, as in \citet{hummels2007}. The database we use to construct our measure of transport costs comes from the US annual ``Imports of Merchandise'' provided by the US Census Bureau, spanning 1974 to 2019 (details on the database provided in Appendix \ref{app:data}). We first use customs values, quantities and freight costs to recover free alongside ship (fas) and cost-insurance-freight (cif) prices, by good, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob (free on board) price rather than the fas price. The fas price means that the seller must transport the goods all the way to the dock, close enough to be reached by the crane of the ship it will be transported in. It is also the seller's responsibility to clear the goods for export. The FOB price means that the seller is obligated to bring the goods all the way to the port, clear the goods for export, and see that they are loaded onto the ship nominated by the buyer. Once the goods clear the railing of the vessel, the buyer assumes the risk. Note that this term is used exclusively for maritime and inland waterway transport. While both terms are closely related, the US Foreign Trade Statistics reports fas prices.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight, \textbf{both items being conditional to the transport mode}; in other words, it is the price for one kg of the goods net of transportation costs, \textbf{by transport mode}. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. \textbf{Cf point 2 refere 1 sur unit prices; avoir quantite plutot que poids, robustesse a faire sur sous-echantillon des produits qui ne passent que par un seul mode de transport).} Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. By construction higher than 1, the variable provides a measure of transport costs as a proportion of the goods' price, an ad-valorem equivalent.
This is quite a standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

Exploiting this dataset also has three advantages.
First, it comes from a single, homogenous and trustworthy customs source.
This limits the measurement error bias.
Based on customs declarations, the US Imports Database inventories all imports (both values and quantities), by country of origin, to the United States at the HS 10-digit level (with a concordance code to the SITC coding system) from \textbf{1989 to 2019}. For the period 1974-1988, we rely on Hummel's original database with a 5-digit product classification level. %This will be crucial to compute transport costs, as we detail below.
In addition, the database reports information regarding freight, insurance and handling expenditures by transportation mode, land/ocean (or ``vessel'') and air.
We will make use of this to highlight potential differences in the dynamics of transport costs across transportation mode.
Second, this dataset provides both the import price and the export price for the same good (for a given origin country).
This is highly valuable, as it gives us a direct measure of international transport costs (at the country/sector level), from which we can estimate separately the \textit{levels} of both the iceberg costs and of the additive costs, in contrast to e.g. \citet{Irrazabal_2015}.
Third, this dataset is available over a long time span, which enables us to analyze the trend patterns of international transport costs over the period \textbf{1989-2019}.\footnote{Note that, as mentioned by \citet{Lafourcade_Thisse}, our transport costs measures are based on actual trade flows, i.e. ignoring those flows that did not happen because of presumably prohibitive transport costs.
In light of this, the estimated values that we obtain can be viewed as the lower bounds of the ``potential'' transport costs.} \smallskip

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. This drives us to estimate international transport costs at the 3-digit classification level, \textbf{exploiting heterogeneity between HS-10 products.} \textbf{La robustesse en 4/10 peut-elle marcher? sur les premieres annees pour lesquelles moins de points - je crois? Que faire de cette analyse 4d?}
However, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years.\footnote{The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013.
Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation.
However, we obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels.
Estimation results at the 4-digit classification level are reported in Appendix \ref{app:4digit}.} Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin.

@@

\paragraph{Estimation strategy} Our purpose is to provide time-varying estimates of the size of ad-valorem transport costs and additive transport costs.
To do so, denote by $p$ the price per kg of goods paid by the importer (import, or cif price), $\widetilde{p}$ the (per kg) export (or fas) price and $f$ the shipping charge per kg shipped. In accordance with \citet{hummels2010}, assume that shipping charges may depend on the price $\widetilde{p}$, such that per kg shipping charges are written as $f = \widetilde{p}^{1-\beta} X$, where $X$ represents all other elements of transport costs (such as distance, port quality, etc.). In this case, the link between the import, export prices and shipping charges is given by:

@@

\textbf{While many in the related literature provide an indirect measure of additive costs by estimating the elasticity of freight charges to the unit price (\citealp{hummels_skiba}, \citealp{Lashkaripour-2018}), thereby relying on Equation (\ref{eq:alternative}), we propose an alternative route. Based on Equation (\ref{base}), we exploit our dataset to obtain explicit measures of both transport costs components $\tau$ and $t$ (or $\widetilde{t}$). From this, we can deduce the price-elasticity of transport costs as the share of additive costs in total transport costs, through Equation (\ref{eq:tt2}).}\smallskip

@@

\begin{equation}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = (1+\tau_{ik}) +\frac{t_{ik}}{ \widetilde{p}_{ik}} \label{eq:base_estimee}
\end{equation}

\textbf{stop here}
